SU($n$) spin models near the Heisenberg critical point

### 2020-03-22 collective_sun/sun_perturbation.tex
fixed derivation of multi-body eigenvalue problem to account for operators that are not permutationally symmetric

\red{[TODO: fix derivation below to account for operators $X$ that are
  not permutationally symmetric]}

@@

$p,q\in k$ or $p,q\notin k$, leaving terms at each fixed $k$ of the
form

@@

  - \sum_{\substack{p\in k\\q\notin k}} h_{pq}

@@

remainder with the complementary restriction.  The terms in

>>>>

\red{[TODO: verify that the derivation below properly accounts for
  operators $X$ that are not permutationally symmetric]}

@@

$p,q\notin k$.  When $p,q\in k$, this permutation operator swaps the
positions of $p$ and $q$ in $X_k$, but we can simply relabel
$\p{p,q}\leftrightarrow\p{q,p}$ with no consequence for $w_k$, so
  \sum_{\substack{k\in\C_N\p{M}\\\p{p,q}\in\C_N\p{2}\\
      p,q\notin k~\t{or}~p,q\in k}}
  = \sum_{k\in\C_N\p{M}}
  \sum_{\substack{\p{p,q}\in\C_N\p{2}\\p,q\notin k~\t{or}~p,q\in k}}
  h_{pq} w_k X_k \ket\psi.
For fixed $k\in\C_N\p{M}$, we can simplify

@@

  - \sum_{\substack{p\in k\\q\in\ZZ_N\setminus k}} h_{pq}

@@

remainder with the complementary restriction; and $E_0$ is the
interaction energy of PS states $\ket\psi\in\M_0$.  The terms in
